Crowd density estimation from Wi-Fi positioning data in the Amsterdam Arena

### 2016-06-28 PaperOnSmoothing/draft-31052016.tex
MAC randomization in methods section

To address the last issue, {\it MAC address randomization}, we rely once again on the law of the large numbers. 
*******end from Sonja

>>>>

To address the last issue, {\it MAC address randomization}, we rely once again on the fact that we have a lot of data. Namely, we know from the structure of the MAC address whether it is randomized or not. Figure \ref{fig:randomized} shows the ratio between randomized and non-randomized addresses observed per minute from midnight until 6:00 am. We can see that it is quite stable through time; in fact, the Pearson correlation coefficient between the time series of randomized and non-randomized addresses is 0.88.

\begin{figure}[h!]
	\centering
	\includegraphics[width=130mm]{RatioRandNonrand.jpeg}
	\caption{Estimations of x-coordinates of a static MAC device as a function of time}
	\label{fig:randomized}
\end{figure}

Thus, when estimating crowd density, we ignore the MAC devices that have a randomized address and at the end we multiply the crowd density by 1.0225, to account for the ignored MAC devices. We choose factor 1.0225 to allow for a safety margin: in the peaks of the graph in Fig. \ref{fig:randomized} the values are 0.025, and we would rather overestimate than underestimate the crowd density. 
Note that this ratio should be re-computed periodically, to account for the changing conditions at the smart phones market.

*******end from Sonja
